---
title: "My Personal portfolio"
author: "Elior Bliah"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    df_print: kable
    results: show
    theme: flatly
    toc: TRUE
    toc_float: TRUE
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE, include=FALSE}
library(quantmod)
library(PerformanceAnalytics)
library(dygraphs)
library(xts)
library(zoo)
library(tidyverse)
library(dplyr)
library(lubridate)
library(plotly) # To create interactive charts
library(timetk)
library(tidyquant)# To manipulate the data series
library(ggcorrplot)
library(zoo)
library(kableExtra)
library(formattable)
library(quantmod)
```

## List of financial assets
```{r message=FALSE, warning=FALSE}

tickers <- c('INTC','JETS','IBCD.DE','WIX','SE','SPY','SEDG','SPEN.TA','ENLT.TA','ELRN.TA','SHOM.TA')
price_data <- tq_get(tickers,
                     from = '2020-01-01',
                     to = as.Date(now()),
                     get = 'stock.prices')

log_ret_tidy <- price_data %>%
  group_by(symbol) %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = 'daily',
               col_rename = 'ret',
               type = 'log')

#spread the data
log_ret_xts <- log_ret_tidy %>%
  spread(symbol, value = ret) %>%
  na.omit() %>%
  tk_xts() %>% as.data.frame()

spy <- log_ret_xts %>%
  select(SPY)


log_ret_xts <- log_ret_xts %>%
  select(-'SPY')

mean_ret <- colMeans(log_ret_xts)

## "Market Capitalization"
cap<- getQuote(tickers, what = yahooQF(c( "Earnings/Share", 
         "P/E Ratio", "Book Value", "EBITDA", "52-week Range")))
cap %>%
  na.omit() %>%
  as.data.frame() %>%
   select(-`Trade Time`) %>%
  kbl() %>%
   kable_classic(full_width = F, html_font = "Cambria",  position = "left")

```
**note** : Missing data for certain companies

# My Israeli stocks

**note** :Loess regression for each stock
```{r message=FALSE, warning=FALSE}
price_data %>%
  subset(symbol == c('SPEN.TA','ENLT.TA','ELRN.TA','SHOM.TA')) %>%
  ggplot(aes(x=date, y= adjusted, color = symbol))+ geom_line()+ geom_smooth(method = "loess") + scale_y_log10()
```

# My stocks in Wall St. 

```{r message=FALSE, warning=FALSE}
price_data %>%
  subset(symbol == c('INTC','JETS','IBCD.DE','WIX','SE','SEDG')) %>%
  ggplot(aes(x=date, y= adjusted, color = symbol))+ geom_line()+ geom_smooth(method = "loess") + scale_y_log10()
```

## Correlation Matrix
```{r message=FALSE, warning=FALSE}
cov_mat <- cov(log_ret_xts) * 252

corr_mat<- round(cor(log_ret_xts), 1)
ggcorrplot(corr_mat, hc.order = TRUE, type = "lower",
   lab = TRUE)
```


To calculate the portfolio returns and risk (standard deviation) we will need

1. Mean assets returns
2. Portfolio weights
3. Covariance matrix of all assets
4. Random weights


we will assume 0.09% risk free rate to calculate the Sharpe Ratio (3 month T-bills)
We have everything we need to perform our optimization. All we need now is to run this code on 5000 random portfolios. For that we will use a for loop.

Before we do that, we need to create empty vectors and matrix for storing our values. The code is as the follow (with some explianations)

#### creation of 5000 portfolio with random weights
```{r message=FALSE, warning=FALSE}

# create random weights first
wts <- runif(n = length(tickers)-1)
wts <- wts/sum(wts)

## calculate the annualized portfolio returns

port_returns <- (sum(wts * mean_ret) + 1)^252 - 1


# Next we will calculate the portfolio risk (Standard deviation). This will be annualized Standard deviation for the portfolio. We will use linear algebra to calculate our portfolio risk.

port_risk <- sqrt(t(wts) %*% (cov_mat %*% wts))

sharpe_ratio <- as.numeric(port_returns-0.0009)/port_risk %>%
  as.data.frame() %>%
  rename( sharpe_ratio = V1) 

num_port <- 5000

# Creating a matrix to store the weights

all_wts <- matrix(nrow = num_port,
                  ncol = length(tickers)-1)

# Creating an empty vector to store
# Portfolio returns

port_returns <- vector('numeric', length = num_port)

# Creating an empty vector to store
# Portfolio Standard deviation

port_risk <- vector('numeric', length = num_port)

# Creating an empty vector to store
# Portfolio Sharpe Ratio

sharpe_ratio <- vector('numeric', length = num_port)

for (i in seq_along(port_returns)) {
  
  wts <- runif(length(tickers)-1)
  wts <- wts/sum(wts)
  
  # Storing weight in the matrix
  all_wts[i,] <- wts
  
  # Portfolio returns
  
  port_ret <- sum(wts * mean_ret)
  port_ret <- ((port_ret + 1)^252) - 1
  
  # Storing Portfolio Returns values
  port_returns[i] <- port_ret
  
  
  # Creating and storing portfolio risk
  port_sd <- sqrt(t(wts) %*% (cov_mat  %*% wts))
  port_risk[i] <- port_sd
  
  # Creating and storing Portfolio Sharpe Ratios
  # Assuming 0% Risk free rate
  
  sr <- port_ret/port_sd
  sharpe_ratio[i] <- sr
  
}

# Storing the values in the table
portfolio_values <- tibble(Return = port_returns,
                  Risk = port_risk,
                  SharpeRatio = sharpe_ratio)


# Converting matrix to a tibble and changing column names
all_wts <- tk_tbl(all_wts)

colnames(all_wts) <- colnames(log_ret_xts)

# Combing all the values together
portfolio_values <- tk_tbl(cbind(all_wts, portfolio_values))
```

Next, lets look at the portfolios that matter the most.


## The Minimum Variance Portfolio


```{r}
min_var <- portfolio_values[which.min(portfolio_values$Risk),]
max_sr <- portfolio_values[which.max(portfolio_values$SharpeRatio),]

p <- min_var %>%
  gather(names(min_var)[1]:names(min_var)[ncol(min_var)-3], key = Asset,
         value = Weights) %>%
  mutate(Asset = as.factor(Asset)) %>%
  ggplot(aes(x = fct_reorder(Asset,Weights), y = Weights, fill = Asset)) +
  geom_bar(stat = 'identity') +
  theme_minimal() +
  labs(x = 'Assets', y = 'Weights', title = "Minimum Variance Portfolio Weights") +
  scale_y_continuous(labels = scales::percent) 

ggplotly(p)


```


## The tangency portfolio 

(the portfolio with highest sharpe ratio)


```{r}
p <- max_sr %>%
  gather(names(min_var)[1]:names(min_var)[ncol(min_var)-3], key = Asset,
         value = Weights) %>%
  mutate(Asset = as.factor(Asset)) %>%
  ggplot(aes(x = fct_reorder(Asset,Weights), y = Weights, fill = Asset)) +
  geom_bar(stat = 'identity') +
  theme_minimal() +
  labs(x = 'Assets', y = 'Weights', title = "Tangency Portfolio Weights") +
  scale_y_continuous(labels = scales::percent) 

ggplotly(p)
```


## The Efficient Frontier

```{r}
p <- portfolio_values %>%
  ggplot(aes(x = Risk, y = Return, color = SharpeRatio)) +
  geom_point() +
  theme_classic() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(labels = scales::percent) +
  labs(x = 'Annualized Risk',
       y = 'Annualized Returns',
       title = "Portfolio Optimization & Efficient Frontier") +
  geom_point(aes(x = Risk,
                 y = Return), data = min_var, color = 'red') +
  geom_point(aes(x = Risk,
                 y = Return), data = max_sr, color = 'red') +
  annotate('text', x = 0.20, y = 0.42, label = "Tangency Portfolio") +
  annotate('text', x = 0.18, y = 0.01, label = "Minimum variance portfolio") +
  annotate(geom = 'segment', x = 0.14, xend = 0.135,  y = 0.01, 
           yend = 0.06, color = 'red', arrow = arrow(type = "open")) +
  annotate(geom = 'segment', x = 0.22, xend = 0.2275,  y = 0.405, 
           yend = 0.365, color = 'red', arrow = arrow(type = "open"))
  

ggplotly(p)
```


#### Purchased stocks
```{r message=FALSE, warning=FALSE, include= FALSE}
ORL.TA <- 101
AYX <- 111.3699
INTC  <- 49.6778
JETS  <- 17.895
WIX  <- 311.5599
SPEN.TA <- 2227
IBCD.DE <-109.96
SGOL<- 15.87
MMM <- 153.25
SE <- 160.39
SEDG <- 262
ENLT.TA <- 646.2
ELRN.TA <- 1068.0
SHOM.TA <- 875

ORL.TA_BD <- dmy("20/04/2020") 
AYX_BD <- dmy("09/09/2020")
INTC_BD <-dmy("09/09/2020")
JETS_BD <-dmy("09/09/2020")
WIX_BD <-dmy("05/08/2020")
SPEN.TA_BD <-dmy("13/01/2020")
IBCD.DE_BD <- dmy("09/09/2020")
SGOL_BD <- dmy("27/02/2020")
MMM_BD <- dmy("27/02/2020")
SE_BD <- dmy("30/10/2020")
SEDG_BD <- dmy("30/10/2020")
ENLT.TA_BD <- dmy("22/11/2020")
ELRN.TA_BD <- dmy("22/11/2020")
SHOM.TA_BD <- dmy("22/11/2020")
```



## Summary of my current holdings

```{r message=FALSE, warning=FALSE}
#buy prices


buy<-data.frame(symbol = c("ORL.TA", "AYX", "INTC", "JETS", "WIX", "SPEN.TA", "IBCD.DE", "MMM", "SGOL", "SE", "SEDG", "ENLT.TA", "ELRN.TA", "SHOM.TA"), 
                 buy_date = c(ORL.TA_BD,   AYX_BD, INTC_BD, JETS_BD, WIX_BD, SPEN.TA_BD, IBCD.DE_BD, SGOL_BD, MMM_BD,SE_BD, SEDG_BD,ENLT.TA_BD, ELRN.TA_BD, SHOM.TA_BD),
                buy_price = c(ORL.TA, AYX,INTC, JETS, WIX, SPEN.TA, IBCD.DE, MMM, SGOL, SE, SEDG, ENLT.TA, ELRN.TA, SHOM.TA)
               )


na.locf2 <- function(x) na.locf(x, na.rm = FALSE)

current_prices <- price_data %>% select(symbol, date, adjusted) %>% 
  group_by(symbol) %>% do(na.locf2(.)) %>% ungroup %>% 
  spread(symbol, adjusted) %>% 
  slice(which.max(as.Date(date, '%d/%m/%Y'))) %>%
  as.data.frame()
  
updated<- current_prices$date  

current_prices <- current_prices %>%
  select(-date) %>%
  gather()

current_prices<- data_frame( rep(updated, nrow(current_prices)),  current_prices) %>%
  rename(current_date = 'rep(updated, nrow(current_prices))')


  table2<- merge.data.frame(buy, current_prices, by.x = "symbol", by.y = "key") %>%
    rename(current_price = value) %>%
    mutate(  "total return" = (current_price/buy_price-1)) %>%
    mutate(  "Holding time (M)" = as.numeric(current_date - buy_date)/30.42) %>%
    mutate("return per month" = `total return`/ `Holding time (M)`)
    
table2 %>%
  kbl(digits = 3) %>%
   kable_classic(full_width = F, html_font = "Cambria",  position = "left") %>%
  column_spec(6, color = "white",
              background = spec_color(table2$`total return`, end = 0.7),
              popover = paste("am:", mtcars$am[1:8]))


  

```


## Sold stocks summary
```{r message=FALSE, warning=FALSE}
SGOL_SP <- 19.61
MMM_SP <- 154.96
AYX_SP <- 144.61
ORL.TA_SP <- 66.8


SGOL_SD <- dmy("05/08/2020")
MMM_SD <- dmy("05/08/2020")
AYX_SD <- dmy("06/10/2020")
ORL.TA_SD <- dmy("10/08/2020")



sold <-data.frame(symbol = c("SGOL","MMM","AYX","ORL.TA"),
                sold_date = c(SGOL_SD,MMM_SD,AYX_SD, ORL.TA_SD ), 
                sold_price = c(SGOL_SP,MMM_SP,AYX_SP,ORL.TA_SP))

  table3<- merge.data.frame(buy, sold, by.x = "symbol", by.y = "symbol") %>%
    mutate(  "total return" = (sold_price/buy_price-1)) %>%
    mutate(  "Holding time (M)" = as.numeric(sold_date - buy_date)/30.42) %>%
    mutate("return per month" = `total return`/ `Holding time (M)`)
    
table3 %>%
  kbl() %>%
   kable_classic(full_width = F, html_font = "Cambria",  position = "left") %>%
  column_spec(6, color = "white",
              background = spec_color(table2$`total return`, end = 0.7),
              popover = paste("am:", mtcars$am[1:8]))


```


## Last week comparison: Portfolio vs Benchmark 
*Note*: only for current holdings

```{r message=FALSE, warning=FALSE}
log_ret_tidy1 <- price_data %>%
  subset(date >  as.Date(now())- 7) %>%
  group_by(symbol) %>%
  tq_transmute(select = adjusted,
               mutate_fun = periodReturn,
               period = 'daily',
               col_rename = 'ret',
               type = 'log')


#spread the data
log_ret_xts1 <- log_ret_tidy1 %>%
  spread(symbol, value = ret) %>%
  tk_xts() %>% as.data.frame()

spy <- log_ret_xts1 %>%
  select(SPY)


log_ret_xts1 <- log_ret_xts1 %>%
  select(-'SPY')

wts_e <- c(rep(1/length(colnames(log_ret_xts1)),length(colnames(log_ret_xts1))))


portfolio_returns_e <- Return.portfolio(R = log_ret_xts1, weights = wts_e, wealth.index = TRUE)


benchmark_returns <- Return.portfolio(R = spy , wealth.index = TRUE)

# Merge the two
comp <- merge.xts(portfolio_returns_e, benchmark_returns)
colnames(comp) <- c("Portfolio", "Benchmark")

# Build an interactive graph to compare performance

comp %>% 
dygraph( main = "Portfolio Performance vs. Benchmark") %>%
  dyAxis("y", label = "Amount ($)")

```





